On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-08-01 paper/paper.tex
Center figure 2 caption
Improved TailRec rewrite
wibble
cleaning up page 2.
reformat for style
Cite Boehm 1985, minor formatting

\begin{todo}
  % Cite examples where Haskell implementations have been derived specifications.  Conal Elliott's latest two papers (as of May 2020), \cite{Elliott-2018-ad-icfp} and \cite{Elliott2019-convolution-extended}, would be good examples of this. (This is now cited)

  A paper which describes a Haskell implementation derived from an operational
  semantics would also be a good example.
\end{todo}

@@

\begin{lstlisting}
data E t where
  ...
  SumMatchExp ::
    (ERep a, ERep b, ERepTy b ~ b)
      => E (ProdMatch a r)
         -> E (SumMatch b r)
         -> E (SumMatch (Either a b) r)

@@

\ttt{E (ProdMatch x y)} is equivalent to a curried function from \ttt{x} to
\ttt{y} in the expression language.  \ttt{s} is a (potentially
nested) pair type. For example, \ttt{E (ProdMatch (a, (b, c)) r)} is
equivalent to \ttt{E (a -> E (b -> E (c -> E r)))}.

@@

Algebraic datatypes can be represented as lambda calculus terms using
\textit{Church encodings}. For example, the pair constructor can be
represented as

@@

These bindings are grouped together in the \ttt{Env} type:

\begin{lstlisting}
newtype Env = Env [EnvMapping]

@@

\section{C Backend}
\label{sec:CBackend}

\begin{todo}
  Should this section be expanded?
\end{todo}

@@

To use this, for example, with the previously mentioned \ttt{isEven} implementation we
can write:

\begin{lstlisting}
isEvenE :: E (Int -> Bool)
isEvenE =
  externalize (
    case x == 0 of
      True -> True
      False ->
        case x == 1 of
          True -> False
          False -> isEvenE (x - 2))

@@

\begin{figure}[hp]

@@

  &C\expr{\ttt{runIter x}} \rewrites \ttt{TailRec $M\expr{\ttt{x}}$}\\

@@

\captionsetup{justification=centering}
\caption{Rewrite rules}
\label{fig:Rewrites}
\end{figure}

@@

\vfill\break

>>>>

\begin{todont}
  % Cite examples where Haskell implementations have been derived specifications.  Conal Elliott's latest two papers (as of May 2020), \cite{Elliott-2018-ad-icfp} and \cite{Elliott2019-convolution-extended}, would be good examples of this. (This is now cited)

  A paper which describes a Haskell implementation derived from an operational
  semantics would also be a good example.
\end{todont}

@@

\newpage
\begin{lstlisting}
data E t where
  ...
  SumMatchExp ::
    (ERep a, ERep b, ERepTy b ~ b)
      => E (ProdMatch a r)
         -> E (SumMatch b r)
         -> E (SumMatch (Either a b) r)

@@

\ttt{E (ProdMatch s t)} is equivalent to a curried function from \ttt{s} to
\ttt{t} in the expression language.  \ttt{s} is a (potentially
nested) pair type. For example, \ttt{E (ProdMatch (a, (b, c)) r)} is
equivalent to \ttt{E (a -> E (b -> E (c -> E r)))}.

@@

Algebraic datatypes can be represented as lambda calculus terms using
\textit{Church encodings}.~\cite{Boehm:1985:AutoSynth} For example, the pair constructor can be
represented as

@@

These bindings are grouped together in the \ttt{Env} type:
\newpage
\begin{lstlisting}
newtype Env = Env [EnvMapping]

@@

\newpage
\section{C Backend}
\label{sec:CBackend}

\begin{todont}
  Should this section be expanded?
\end{todont}

@@

To use this, for example, with the previously mentioned \ttt{isEven} implementation we
can write:
\newpage
\begin{lstlisting}
isEvenE :: E (Int -> Bool)
isEvenE =
  externalize (
    case x == 0 of
      True -> True
      False ->
        case x == 1 of
          True -> False
          False -> isEvenE (x - 2))

@@

\begin{figure*}[hp]

@@

  &C\expr{\ttt{runIter f x}} \rewrites \ttt{App (TailRec $M\expr{\ttt{f}}$) $M\expr{\ttt{x}}$}\\

@@

\captionsetup{justification=centering}
\caption{Rewrite rules}
\label{fig:Rewrites}
\end{figure*}

@@

% \vfill\break
